\textit{Supporting Information for}: Geometric models reveal behavioral and neural signatures of transforming experiences into memories

### 2020-10-14 paper/supporting_information.tex
removed duplicate page numbering in main text and supplement

\title{\textit{Supporting Information for}: Geometric models reveal behavioral and neural signatures of transforming naturalistic experiences into episodic memories}
\author{Andrew C. Heusser\textsuperscript{1, 2, \textdagger}, Paxton C. Fitzpatrick\textsuperscript{1, \textdagger}, and Jeremy R. Manning\textsuperscript{1, *}\\\textsuperscript{1}Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\\textsuperscript{2}Akili Interactive Labs\\Boston, MA 02110\\\textsuperscript{\textdagger}Denotes equal contribution\\\textsuperscript{*}Corresponding author: Jeremy.R.Manning@Dartmouth.edu}

@@

\begin{document}
\begin{titlepage}
  \maketitle
\end{titlepage}

\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}
\setcounter{section}{0}
\makeatletter
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\bibnumfmt}[1]{[S#1]}
\renewcommand{\citenumfont}[1]{S#1}

\section*{Overview}
This document provides additional details about the methods we used in the main text.  We also include some additional analyses referenced in the main text.

\section*{Additional details about topic modeling methods and results}
\subsection*{Optimizing topic model parameters}
In order to create accurate episode and recall models, we used an optimization method that was driven by our ability to explain hand-annotated memory performance metrics collected by \cite{ChenEtal17}.  In an earlier variant of our study~\citep{HeusMann18}, we used a grid search to compute the $\omega$ (episode sliding window duration, in scenes), $\rho$ (recall sliding window duration, in sentences), and $K$ (number of topics) that satisfied
\[
\argmax_{\omega, \rho, K} \left[\mathrm{corr}\left(\mathrm{corr}\left(\mu\left(\omega, \rho, K\right), \nu\left(\omega, \rho, K\right)\right), \theta\right)\right],
\]
where $\mathrm{corr}(\mu, \nu)$ is the per-participant correlation between the episode ($\mu$) and recall ($\nu$) topic proportions matrices, and $\theta$ is the per-participant hand-counted number of recalled scenes.  We searched over a grid of pre-specified values for each of these parameters; the resulting correlations are displayed in Figure~\ref{fig:paramsearch}.  The optimal parameters were $\omega = 50$, $\rho = 10$, and $K = 100$.  In our current paper we made a number of improvements to how we preprocessed text and fit topic models (see \textit{Methods}), but we carried the same optimal parameters forward from \cite{HeusMann18} without performing any additional optimization.

@@

% \FloatBarrier
\newpage
\begin{centering}
 \vspace*{\fill}
    \section*{Participant-level figures referenced in the main text}
    \vspace*{\fill}
  \end{centering}

@@

\newpage
\renewcommand{\refname}{Supplemental references}
\bibliography{CDL-bibliography/memlab}

>>>>

\title{\textit{Supporting Information for}: Geometric models reveal behavioral and neural signatures of transforming experiences into memories}
\author{Andrew C. Heusser\textsuperscript{1, 2, \textdagger}, Paxton C. Fitzpatrick\textsuperscript{1, \textdagger}, and Jeremy R. Manning\textsuperscript{1, *}\\\textsuperscript{1}Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\\textsuperscript{2}Akili Interactive Labs\\Boston, MA 02110, USA\\\textsuperscript{\textdagger}Denotes equal contribution\\\textsuperscript{*}Corresponding author: Jeremy.R.Manning@Dartmouth.edu}

@@

\begin{document}

\renewcommand{\figurename}{Supplementary Figure}

%\begin{titlepage}
%  \maketitle
%  \thispagestyle{empty}
%\end{titlepage}

\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}
\setcounter{section}{0}
\makeatletter
%\renewcommand{\theequation}{S\arabic{equation}}
%\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\bibnumfmt}[1]{[S#1]}
\renewcommand{\citenumfont}[1]{S#1}

%\section*{Overview}
%This document provides additional details about the methods we used in the main text.  We also %include some additional analyses referenced in the main text.

\section*{Supplementary methods}
\subsection*{Optimizing topic model parameters}
In order to create accurate episode and recall models, we used an optimization method that was driven by our ability to explain hand-annotated memory performance metrics collected by \cite{ChenEtal17}.  In an earlier variant of our study~\citep{HeusMann18}, we used a grid search to compute the $\omega$ (episode sliding window duration, in scenes), $\rho$ (recall sliding window duration, in sentences), and $K$ (number of topics) that satisfied
\[
\argmax_{\omega, \rho, K} \left[\mathrm{corr}\left(\mathrm{corr}\left(\mu\left(\omega, \rho, K\right), \nu\left(\omega, \rho, K\right)\right), \theta\right)\right],
\]
where $\mathrm{corr}(\mu, \nu)$ is the per-participant correlation between the episode ($\mu$) and recall ($\nu$) topic proportions matrices, and $\theta$ is the per-participant hand-counted number of recalled scenes.  We searched over a grid of pre-specified values for each of these parameters; the resulting correlations are displayed in Figure~\ref{fig:paramsearch}.  The optimal parameters were $\omega = 50$, $\rho = 10$, and $K = 100$.  In our current paper we made a number of improvements to how we preprocessed text and fit topic models (see \textit{Methods}), but we carried the same optimal parameters forward from \cite{HeusMann18} without performing any additional optimization.

@@

% \FloatBarrier
\newpage
\begin{centering}
  \vspace*{\fill}
  \section*{Supplementary figures}
    \subsection*{Participant-level figures referenced in the main text}
    \vspace*{\fill}
  \end{centering}

@@

\newpage
\renewcommand{\refname}{Supplementary references}
\bibliography{CDL-bibliography/memlab}
